Impact of grids and dynamical cores in CESM2.2 on the surface mass balance of the Greenland Ice Sheet

### 2022-05-06 arcticgrids.tex
new figs

\begin{figure}[t]
\begin{center}
\begin{tabular}{ccc}
         \includegraphics[width=40mm]{figs/grid-ARCTIC.pdf}&
         \includegraphics[width=40mm]{figs/grid-ARCTICGRIS.pdf}&
         \includegraphics[width=40mm]{figs/grid-CONUS.pdf} \\
\end{tabular}
\end{center}
\caption{Spectral-element grid for the VR grids in this study, (a) $\tt Arctic$, (b) $\tt Arctic-GrIS$ and (c) $\tt CONUS$. Note that this is not the computational grid; each element has $3\times3$ independent grid points.}
\label{fig:vr-grids}
\end{figure}

@@

Figure~\ref{fig:tseries} shows time series of annually integrated precipitation and snow/ice melt over the GrIS for the various different grids and dycores, and RACMO in black. The 1979-1998 climatological mean values, listed in Table~\ref{tbl:table3}, are shown as circles on the right side of the panels. The uniform $1^{\circ}-2^{\circ}$ grids have positive precipitation biases, whereas the VR grids have the smallest biases, with precipitation comparable to RACMO. The $\tt f19$ and $\tt f09$ grids perform similarly, with +110 Gt/yr bias, whereas $\tt ne30pg3$ is biased by about +165 Gt/yr and $\tt ne30pg2$ by +230 Gt/yr. The larger biases on the uniform-resolution SE grids relative to the FV grids are consistent with the coarser GrIS resolution on the SE grids (Figure~\ref{fig:grisdx}).

>>>>

\begin{figure}[t]
\begin{center}
\begin{tabular}{ccc}
         \includegraphics[width=40mm]{figs/grid-ARCTIC.pdf}&
         \includegraphics[width=40mm]{figs/grid-ARCTICGRIS.pdf}&
         \includegraphics[width=40mm]{figs/grid-CONUS.pdf} \\
\end{tabular}
\end{center}
\caption{Variable-resolution grids available in CESM2.2, (a) $\tt Arctic$, (b) $\tt Arctic-GrIS$ and (c) $\tt CONUS$. Note what is shown is the element grid; the computational grid has $3\times3$ independent grid points per element.}
\label{fig:vr-grids}
\end{figure}

@@

Figure~\ref{fig:tseries} shows time series of annually integrated precipitation and snow/ice melt over the GrIS for the various different grids and dycores, and RACMO in black. The 1979-1998 climatological mean values from Table~\ref{tbl:table3} are shown as circles on the right side of the panels. The uniform $1^{\circ}-2^{\circ}$ grids have positive precipitation biases, whereas the VR grids have the smallest biases, with precipitation comparable to RACMO. The $\tt f19$ and $\tt f09$ grids perform similarly, with +110 Gt/yr bias, whereas $\tt ne30pg3$ is biased by about +165 Gt/yr and $\tt ne30pg2$ by +230 Gt/yr. The larger biases on the uniform-resolution SE grids relative to the FV grids are consistent with the coarser GrIS resolution on the SE grids (Figure~\ref{fig:grisdx}).
